SeedLing: Building and using a seed corpus \\ for the Human Language Project

### 2014-04-28 docs/computEL-final/data.tex
Michaela's affiliation, and small edits

Out of our data sources, three can be straightforwardly represented in their aligned text structure. However, ODIN contains richer annotations, which are in fact difficult to fit into their proposal, and which we discuss in section \ref{sec:odin} below.

>>>>

Out of our data sources, three can be straightforwardly represented in the aligned text structure. However, ODIN contains richer annotations, which are in fact difficult to fit into Abney and Bird's proposal, and which we discuss in section \ref{sec:odin} below.

### 2014-04-28 docs/computEL-final/paper.tex
Michaela's affiliation, and small edits

\author{Guy Emerson, Liling Tan, Susanne Fertmann, Alexis Palmer and Michaela Regneri \\
Universität des Saarlandes \\
66123 Saarbrücken, Germany \\
{\tt \{emerson, liling, susfert, apalmer, regneri\}} \\
{\tt @coli.uni-saarland.de} \\
}
\date{}

>>>>

\author{Guy Emerson, Liling Tan, \\ \textbf{Susanne Fertmann, Alexis Palmer} \\
Universität des Saarlandes \\
66123 Saarbrücken, Germany \\
{\tt \{emerson, liling, susfert,} \\ {\tt apalmer\} @coli.uni-saarland.de} \\\And
Michaela Regneri \\
IT-Department \\
SPIEGEL-Verlag \\
Hamburg, Germany \\
{\tt michaela\_regneri@spiegel.de}}

\date{}
